### 2022-09-19 chapters/introduction.tex

\chapter{Motivation \note{missing}}

@@

Nowadays, computers are invading our daily lives, from work to leisure, from fancy smartphones to an embedded peacemaker that regulates the heartbeat of people.
As human beings, we are known to use tools to enhance our bodies. And thanks to computers, we pushed that step even further, to the point where now we are using machines to extend our brains. Some even argue that one day they will replace us, and therefore we have created our own ending.

Well, this is the problem for the future generations. For the moment, the main concern of humanity is to keep this planet liveable until we find another alternative.

>>>>

@@

Nowadays, computers are invading our daily lives, from work to leisure, from fancy smartphones to an embedded peacemaker that regulates the heartbeat of people.
As human beings, we are known to use tools to enhance our bodies. And thanks to computers, we pushed that step even further, to the point where now we are using machines to extend our brains. Some even argue that one day they will replace us, and therefore we have created our own ending.
?
https://www.iea.org/reports/data-centres-and-data-transmission-networks

The Internet of Things (IoT) is one of the most popular topics in computer science and engineering, and it is expected to be a very important part of our lives in the future
However, the energy consumption of ICT equipment is also expected to increase, from 4.3 exajoules in 2018 to 5.8 exajoules in 2025, according to [17].
[17]: https://www.statista.com/statistics/271139/energy-consumption-of-ict-worldwide/
Well, this is the problem for the future generations. For the moment, the main concern of humanity is to keep this planet liveable until we find another alternative.

The number of data centers is expected to increase from 1.6 million in 2018 to 2.1 million in 2025, according to [16].
[16]: https://www.statista.com/statistics/271138/number-of-data-centers-worldwide/

The number of people connected to the Internet has increased by 4.4 billion in 2019, reaching 4.54 billion worldwide, or 59.2\% of the world population, according to the Internet World Stats [14].
[14]: https://www.internetworldstats.com/stats.htm

\begin{figure}
    \includegraphics[width=\linewidth]{chapters/distribution_of_ict_consumption.png}
    \caption{Final energy consumption of digital technologies by item in 2017}
    \label{fig:soa_comparaisoncpu}
\end{figure}

All these new activities have increased the overall environmental footprint of the Information and Communication Technology (ICT) sector, which is estimated to be responsible for approximately 4\% of the greenhouse gaz (GHG) emissions worldwide in 2020 with a worrying 8\% growth rate, according to the French think tank The Shift Project [137], or 2\% according to [13], a similar number to the aviation sector contribution.
    [137]: https://www.theshiftproject.org/article/ict-environmental-impact/
[13]: https://www.theguardian.com/environment/2020/jan/06/tech-industry-emissions-soar-at-double-rate-of-aviation-and-shipping
